Deep learning approaches on musical assisted-orchestration: an evaluation study

### 2020-05-01 paper/latex/paper.tex
Put in Carmine's notes for each section

\section{Our model}

@@

\subsection{ResNet}

\section{Orchestration experiments}
List of experiments:

- CNN with varying n

- ResNet with n=10

\section{Evaluation and Conclusions}

\subsection{Interpreting the Latent Space}

\section{Future steps}

>>>>

\section{Our model}
- deep learning trained for classification and then used for orchestraion
- changing number of instruments

@@

\subsection{ResNet}
- SVM was good but CNN was better and ResNet was best
- review all experiments we did and choose key plots

\section{Orchestration experiments}
- set of 10 targets
- orchestra fix to 10
- qualitative evaluation: acoustic inspection of the solutions
- quantitative evaluation: distance in feature space
- comparison table between Orchidea and our model

We performed experiments varying the number instruments used to form combinations, and varying the number of instruments used in each combination. (insert table of data showing the results of CNN with 2,3,4 etc instruments). An arbitrary number of samples can be used in the solution, since the $n$ highest probabilities can be taken from the output, leading to $n$ samples in the solution.

We tested our models using 15 targets for orchestration. These targets are not made from combinations of the input data, and some are not even recordings of instruments. Among the targets are recordings of bells, a car horn, a gong, and an environmental recording of a boat docking. By passing these samples into a model, an orchestration of the target is created from the TinySOL samples that were used to train the network.

\section{Evaluation and Conclusions}
- the approach seems promising for orchestration
- many things used in Orchidea are not implemented here (symbolic constraints, sparsity,...)
- CNN seems better for timbre
- ResNet seems better for pitch (what are timbre and pitch??)

\subsection{Interpreting the Latent Space}
- the system finds filters like...

\section{Future steps}
- using conditioning to impose symbolic constraints
- variable size solutions
- joint networks for orchestral size detection and orchestral families (see paper)
